---
title: "purge_map_all_years"
author: "Reina Kishida"
date: "2025-09-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Setup
pacman::p_load(spdep, sf, tidyverse, ggplot2, here, readxl)

output_dir <- here("..", "..", "output", "fig")
dir.create(output_dir, showWarnings = FALSE)
```


```{r}
# purge statistics
pref_level_purges <- read_excel(here("..", "..", "data", "raw", "prefecture_level_purges.xlsx")) 
# %>% 
#   mutate(prefecture = if_else(prefecture == "Hyõgo", "Hyogo", if_else(prefecture == "Kaganawa", "Kanagawa", prefecture)))

# map data
japan_map <- st_read(here("..", "..", "data", "raw", "JPN_adm", "JPN_adm2.shp")) %>% 
  mutate(NAME_1 = if_else(NAME_1 == "Hyōgo", "Hyogo", if_else(NAME_1 == "Naoasaki", "Nagasaki", NAME_1)))

# election candidates
election_1946 <- read_excel(here("..", "..", "data", "raw", "election_lower_1946.xlsx"))
election_1947 <- read_excel(here("..", "..", "data", "raw", "election_both_1947.xlsx"))

# Dissolve polygons by prefecture code
japan_map_pref_level <- japan_map %>%
  group_by(ID_1, NAME_1) %>%
  summarize(geometry = st_union(geometry)) %>%
  ungroup()

# merge
df_purge_map <- japan_map_pref_level %>%
  left_join(pref_level_purges, by = c("NAME_1" = "prefecture")) %>%
  mutate(reg_purge_rate = (registered_purgees / population) * 100,
         est_purge_rate = (estimated_purgees / population) * 100,
         reg_purge_per_k = (registered_purgees / population) * 1000,
         est_purge_per_k = (estimated_purgees / population) * 1000,
         ) %>% 
  rename(pref_ID = ID_1,
         prefecture = NAME_1) 

# 1946 election data
df_purge_map <- df_purge_map %>% 
  left_join(election_1946, by = c("area", "prefecture")) %>% 
  mutate(
    reg_purge_l46 = (registered_purgees / candidates_lower_1946),
    est_purge_l46 = (estimated_purgees / candidates_lower_1946)
  ) 

# 1947 election data
df_purge_map <- df_purge_map %>%
  left_join(election_1947, by = c("area", "prefecture")) %>% 
  mutate(
    reg_purge_l47 = (registered_purgees / candidates_lower_1947),
    est_purge_l47 = (estimated_purgees / candidates_lower_1947)
  ) %>% 
  mutate(
    reg_purge_u47_large = (registered_purgees / candidates_upper_1947_large),
    est_purge_u47_large = (estimated_purgees / candidates_upper_1947_large),
    reg_purge_u47_middle = (registered_purgees / candidates_upper_1947_middle),
    est_purge_u47_middle = (estimated_purgees / candidates_upper_1947_middle)
  )
# 
# df_purge_map <- df_purge_map %>% 
#   rename(
#     candidates_upper_large_1947 = candidates_upper_1947,
#     reg_purge_per_cand_u47_large = reg_purge_per_candidate_u47,
#     est_purge_per_cand_u47_large = est_purge_per_candidate_u47
#   )

```


# map 1: Registered purge density (%)

```{r}
map1 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = reg_purge_rate), color = "white") +
  # scale_fill_viridis_c(option = "plasma", na.value = "grey90", name = "Registered Purge Rate (%)") +
  scale_fill_gradient(low = "lightgreen", high = "darkgreen", na.value = "grey90", name = "Purge rate (%)") +
  theme_minimal() +
  labs(title = "Purge Rate (%)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("reg_purge_rate", ".png")), 
       plot = map1, 
       width = 6, height = 4,
       dpi = 300, bg = "white")

```

# map 2: Estimated purge density (%)

```{r}
# map 2
map2 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = est_purge_rate), color = "white") +
  # scale_fill_viridis_c(option = "plasma", na.value = "grey90", name = "Estimated Purge Rate (%)") +
  scale_fill_gradient(low = "lightgreen", high = "darkgreen", na.value = "grey90", name = "Purge rate (%)") +
  theme_minimal() +
  labs(title = "Purge Rate (%)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("est_purge_rate", ".png")), 
       plot = map2, 
       width = 6, height = 4,
       dpi = 300, bg = "white")

```


# map 3: Registered purge density (per 1000 people)

```{r}
map3 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = reg_purge_per_k), color = "white") +
  scale_fill_gradient(low = "lightgreen", high = "darkgreen", na.value = "grey90", name = "Purges per 1000 people") +
  theme_minimal() +
  labs(title = "Purge Rate (per 1000 people)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("reg_purge_per_k", ".png")),
       plot = map3, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```

# map 4: Estimated purge density (per 1000 people)

```{r}
map4 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = est_purge_per_k), color = "white") +
  scale_fill_gradient(low = "lightgreen", high = "darkgreen", na.value = "grey90", name = "Purges per 1000 people") +
  theme_minimal() +
  labs(title = "Purge Rate (per 1000 people)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("est_purge_per_k", ".png")),
       plot = map4, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```

# map 5: Registered purge density (per candidates in 1946 election) (Lower)

```{r}
map5 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = reg_purge_l46), color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey90", name = "Purges per candidate (1946)") + # blue for lower election
  theme_minimal() +
  labs(title = "Purges per Candidate (Lower)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("reg_purge_l46", ".png")),
       plot = map5, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```

# map 6: Estimated purge density (per candidates in 1946 election) (Lower)

```{r}
map6 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = est_purge_l46), color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey90", name = "Purges per candidate (1946)") +
  theme_minimal() +
  labs(title = "Purges per Candidate (Lower)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("est_purge_l46", ".png")),
       plot = map6, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```



# map 7: Registered purge density (per candidates (1947)) (Lower)


```{r}
map7 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = reg_purge_l47), color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey90", name = "Purges per candidate (1947)") + # blue for lower election
  theme_minimal() +
  labs(title = "Purges per Candidate (Lower)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("reg_purge_l47", ".png")),
       plot = map7, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```


# map 8: Estimated purge density (per candidates (1947)) (Lower)

```{r}
map8 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = est_purge_l47), color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey90", name = "Purges per candidate (1947)") +
  theme_minimal() +
  labs(title = "Purges per Candidate (Lower)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("est_purge_l47", ".png")),
       plot = map8, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```


# map 9: Registered purge density (per candidates (1947)) (Upper, Large Constituency)

```{r}
map9 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = reg_purge_u47_large), color = "white") +
  scale_fill_gradient(low = "lightpink", high = "darkred", na.value = "grey90", name = "Purges per candidate (1947)") + # blue for lower election
  theme_minimal() +
  labs(title = "Purges per Candidate (Upper, Large)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("reg_purge_u47_large", ".png")),
       plot = map9, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```

# map 10: Estimated purge density (per candidates (1947)) (Upper Large Constituency)

```{r}
map10 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = est_purge_u47_large), color = "white") +
  scale_fill_gradient(low = "lightpink", high = "darkred", na.value = "grey90", name = "Purges per candidate (1947)") +
  theme_minimal() +
  labs(title = "Purges per Candidate (Upper, Large)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("est_purge_u47_large", ".png")),
       plot = map10, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```

# map 11: Registered purge density (per candidates (1947)) (Upper Middle Constituency)

```{r}
map11 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = reg_purge_u47_middle), color = "white") +
  scale_fill_gradient(low = "lightpink", high = "darkred", na.value = "grey90", name = "Purges per candidate (1947)") + # blue for lower election
  theme_minimal() +
  labs(title = "Purges per Candidate (Upper, Middle)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("reg_purge_u47_middle", ".png")),
       plot = map11, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```

# map 12: Estimated purge density (per candidates (1947)) (Upper Middle Constituency)

```{r}
map12 <- ggplot(data = df_purge_map) +
  geom_sf(aes(fill = est_purge_u47_middle), color = "white") +
  scale_fill_gradient(low = "lightpink", high = "darkred", na.value = "grey90", name = "Purges per candidate (1947)") +
  theme_minimal() +
  labs(title = "Purges per Candidate (Upper, Middle)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

ggsave(filename = file.path(output_dir, paste0("est_purge_u47_middle", ".png")),
       plot = map12, 
       width = 6, height = 4,
       dpi = 300, bg = "white")
```

